### 2011-02-10 paper/results.tex
changes

\edit{Jeff: proofread again}

Before optimizing the chosen family of parameterized gaits
(\secref{motionModel}) with learning methods, we performed an
experiment to explore the five dimensions of the SineModel5 parameter
space. Specifically, we selected a random parameter vector that
resulted in some motion, but not an exceptional gait. We then varied
each of the five parameters individually and measured performance,
repeating each measurement twice to get a rough estimate of the
measurement noise at each point.  The results of this exploration,
shown in \figref{explore_dim_1}, reveal that some dimensions ($\amp$,
$\tau$, $m_F$) are fairly smooth and exhibit global structure across
the allowable parameter range, while others ($m_O$, $m_R$) exhibit
more complex behavior.  In addition, it gives a rough indication that
measurement noise is often significant and is more likely to be large
for larger measurements.  Of course, this is only a slice in each
dimension through a single point, and slices through a different point
would produce different behavior.  The common point at the
intersection of all slices is shown as a red triangle in
each plot of \figref{explore_dim_1}.

>>>>

Before optimizing the chosen family of parameterized gaits
(\secref{motionModel}) with learning methods, we performed an
experiment to explore the five dimensions of the SineModel5 parameter
space. Specifically, we selected a random parameter vector that
resulted in some motion, but not an exceptional gait. We then varied
each of the five parameters individually and measured performance,
repeating each measurement twice to get a rough estimate of the
measurement noise at each point.  The results of this exploration,
shown in \figref{explore_dim_1}, reveal that some dimensions ($\amp$,
$\tau$, $m_F$) are fairly smooth and exhibit global structure across
the allowable parameter range, while others ($m_O$, $m_R$) exhibit
more complex behavior.  In addition, it gives a rough indication that
measurement noise is often significant and is more likely to be large
for gaits that move more.  Of course, this is only a slice in each
dimension through a single point, and slices through a different point
could reveal different behavior.  The common point at the
intersection of all slices is shown as a red triangle in
each plot of \figref{explore_dim_1}.
